LAGOS lake depth

### 2021-11-10 README.Rmd
hide docker, link ms

[![Paper DOI](https://img.shields.io/badge/Paper-DOI-blue.svg)](https://doi.org) [![Code DOI](https://img.shields.io/badge/Code-DOI-blue.svg)](https://doi.org/) [![Data DOI](https://img.shields.io/badge/Data-10.6084/m9.figshare.12722246-blue.svg)](https://doi.org/10.6084/m9.figshare.12722246) [![Docker Build](https://img.shields.io/badge/Docker%20Image-jsta/bathymetry-green.svg)](https://cloud.docker.com/repository/docker/jsta/bathymetry)

@@

@@

```shell
# docker

```

>>>>

[![Paper DOI](https://img.shields.io/badge/Paper-DOI-blue.svg)](https://doi.org) [![Code DOI](https://img.shields.io/badge/Code-DOI-blue.svg)](https://doi.org/) [![Data DOI](https://img.shields.io/badge/Data-10.6084/m9.figshare.12722246-blue.svg)](https://doi.org/10.6084/m9.figshare.12722246)

<!--- [![Docker Build](https://img.shields.io/badge/Docker%20Image-jsta/bathymetry-green.svg)](https://cloud.docker.com/repository/docker/jsta/bathymetry) --->

@@

Paper: [manuscript/manuscript.pdf](manuscript/manuscript.pdf)

@@

<!--- ```shell --->
<!--- # TODO: docker --->
<!--- ``` --->
